Democracy, Public Support, and Measurement Uncertainty

### 2021-05-04 paper/dcpo_demsupport.Rmd
corrected the output path
dcpo results

save(result_clsUncertain, file = "estimates_clsAJPS.RDS")
```

```{r dcpoPointAJPS, eval = TRUE}
# ls_country <- levels(dcpo_input$data$kk)
# first_year <- min(dcpo_input$data$year)
# 
# df_dcpoMean <- purrr::map_df(1:1000, function(anEntry) {
#   dcpo_theta$theta[anEntry,,] %>% 
#     reformat_dcpo_output("theta") %>% 
#     left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
#               by = c("year", "country"))
# }) %>% 
#   group_by(country, year) %>% 
#   summarise(theta = mean(theta), 
#             sigma = mean(sigma))
# 
# save(df_dcpoMean, file = here::here("output", "estimates_dcpoMean.RDS"))
df_dcpoMean <- readRDS(here::here("output", "estimates_dcpoMean.RDS"))

@@

tidy_dcpo <- map(df_result_cls, function(result) {
  df_result <- tidy(result, conf.int = TRUE)

@@

glance_dcpo <- map(df_result_cls, function(aResult){
  if(class(aResult) == "plm"){ 
    glance.plm(aResult) # using the customized glance function
  }else{
      glance(aResult)
    }
})

>>>>

save(result_clsUncertain, file = here::here("output", "estimates_clsAJPS.RDS"))
```

```{r dcpoPointAJPS, eval = TRUE}
ls_country <- levels(dcpo_input$data$kk)
first_year <- min(dcpo_input$data$year)

df_dcpoMean <- purrr::map_df(1:1000, function(anEntry) {
  dcpo_theta$theta[anEntry,,] %>%
    reformat_dcpo_output("theta") %>%
    left_join(reformat_dcpo_output(dcpo_sigma$sigma[anEntry,,], "sigma"),
              by = c("year", "country"))
}) %>%
  group_by(country, year) %>%
  summarise(theta = mean(theta),
            sigma = mean(sigma))

# the readRDS produced "unknown format" error, very weild
# save(df_dcpoMean, file = here::here("output", "estimates_dcpoMean.RDS"))
# df_dcpoMean <- readRDS(here::here("output", "estimates_dcpoMean.RDS"))

@@

tidy_dcpo <- map(df_result_dcpo, function(result) {
  df_result <- tidy(result, conf.int = TRUE)

@@

glance_dcpo <- map(df_result_dcpo, function(aResult){
  if(class(aResult) == "plm"){ 
    glance.plm(aResult) # using the customized glance function
  }else{
      glance(aResult)
    }
})
